The 2013 paper written by Ari Juels and Ronald L. Rivest, found  there%[here](http://people.csail.mit.edu/rivest/honeywords/paper.pdf), 
introduces a fascinating way of detecting offline brute-force password-cracking. In a similar style to honeypots, honeywords are stored with the user's password. Should the username/password files be compromised, an adversary is presented with honeywords in addition to a user's genuine password. If this false password is entered into the authentication system with the username, a flag is raised indicating that someone has compromised the files and is attempting to masquerade as the user. \\

Despite being a clever scheme, several problems still remain before an implementation can be successfully deployed. The most pertinent of these problems is the honeywords generation. Given a password, a set of honeywords must be generated in a manner such that the adversary will have the most difficulty in guessing the genuine password from the complete set. The style of password generation or resetting referred to in Rivest's paper called Modern-UI which forces users to adhere to a more strict standard of creating passwords, successfully eliminates the need for this algorithm. However, the logistics and stigma behind forcing users to adhere to a particular pattern of passwords can be infeasable or undesirable. Therefore, this algorithm will accept any given password and produce a set of corresponding honeywords designed to appear as feasible passwords. In this paper, then, we will discuss the techniques used for creating these honeywords and provide justification for them.\\


%% comment
% 2-3 sentences on honeywords, chaffing. The strategies discussed in prior literature leave much room for improvement. Enter HoneyBabel. Chaffing strategies we propose (2-3 sentences). Sentence on our analysis/discussion/conclusion. Sentence on our contribution to this research area.


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "mics_paper"
%%% End: 
